---
title: "mp3"
author: "Yejin Hwang"
date: "11/16/2017"
output: html_document
---

```{r}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
dbListTables(db)
```
```{r}
dbListFields(db,"title")
```
```{r}
titles <- dbGetQuery(db, "SELECT * FROM title LIMIT 0,100;")
View(titles)

db %>%
  tbl("title") %>%
  head(3)
```

```{r}
west<- db %>%
  dbGetQuery("SELECT  mi.movie_id, title, production_year
FROM movie_info mi
LEFT JOIN title t ON mi.movie_id = t.id
LEFT JOIN kind_type kt ON kind_id =  kt.id
WHERE info_type_id = 3 AND info = 'Western' AND kind='movie';")
#save(west,file="Westerns.rda")
#load("Westerns.rda")
#ggplot(west,aes(x=production_year, y=))
```

```{r}
#SELECT t.title, t.production_year, series_years, keyword

west2<- db %>%
  dbGetQuery("SELECT mi.info_type_id, mi.info,mi2.info_type_id, mi2.info,mi1x.info_type_id, mi1x.info,mi2x.info_type_id, mi2x.info
FROM title t
JOIN movie_info AS mi ON t.id = mi.movie_id
JOIN movie_info mi2 ON mi2.movie_id=t.id
JOIN movie_keyword mk on t.id = mk.movie_id
JOIN keyword k ON mk.keyword_id
JOIN movie_info_idx AS mi1x ON mi1x.movie_id = t.id
JOIN movie_info_idx AS mi2x ON mi2x.movie_id = t.id
LEFT JOIN kind_type kt ON kind_id =  kt.id
WHERE mi.info_type_id = 3 AND mi.info='Western' 
AND mi2.info_type_id=4 AND mi2.info='English'
AND kind='movie'
AND t.kind_id = 1
  AND mi1x.info_type_id = 100
  AND mi2x.info_type_id = 101
  AND mi1x.info > 100000
ORDER BY mi2x.info desc;")